\documentclass[a4paper,10pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem, hyperref, parskip}
\usepackage{xcolor}
\usepackage{titlesec}

% Custom colors
\definecolor{headerblue}{RGB}{44, 62, 80}
\definecolor{graytext}{RGB}{96, 96, 96}

% Formatting section titles
\titleformat{\section}{\large\bfseries\color{headerblue}}{}{0em}{}
\titlespacing*{\section}{0pt}{10pt}{6pt}

% Link formatting
\hypersetup{
    colorlinks=true,
    linkcolor=headerblue,
    urlcolor=headerblue
}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{\href{https://myportfolioxznafi.vercel.app/}{Zawad Nafi}}} \\
    \vspace{2mm}
    \small
    \href{mailto:znafi@ualberta.ca}{znafi@ualberta.ca} \hspace{3mm} $\vert$ \hspace{3mm}
    \href{https://www.linkedin.com/in/zawadnafi}{LinkedIn} \hspace{3mm} $\vert$ \hspace{3mm}
    \href{https://github.com/znafi}{GitHub} \hspace{3mm} $\vert$ \hspace{3mm} 825-333-6984\hspace{3mm} $\vert$ \href{https://myportfolioxznafi.vercel.app/}{Portfolio}
\end{center}
\vspace{-4mm}
\hrule \vspace{6pt}

% Education
\section*{Education}
\textbf{Bachelor of Science in Computer Science} \hfill \textit{Expected Graduation: 2027} \\
University of Alberta | Relevant Coursework: Data Structures, Algorithms, Software Engineering
\vspace{6pt}
\hrule \vspace{6pt}

% Technical Skills
\section*{Technical Skills}
\textbf{Programming Languages:} Python, JavaScript, TypeScript, SQL, C++, Motoko \\
\textbf{Technologies:} React, Next.js, Flask, Node.js, Express, Prisma, MongoDB, SQLite, Elasticsearch, Internet Computer \\
\textbf{Tools:} Git, Docker, Postman, VS Code, JIRA, LaTeX \\
\textbf{Methodologies:} Agile, Scrum, CI/CD, Test-Driven Development (TDD)
\vspace{6pt}
\hrule \vspace{6pt}

% Professional Experience
\section*{Professional Experience}

\textbf{Project Manager, ConnectionHub.ca} \hfill \textit{Summer Internship, May - August 2024}
\begin{itemize}[leftmargin=*]
    \item Led project planning and execution, increasing team efficiency by 30\% through Agile methodologies.
    \item Coordinated cross-functional teams to align with business goals, demonstrating ownership and customer obsession.
    \item Managed stakeholder communication, risk assessments, and optimized resource allocation by 20\%.
\end{itemize}

\vspace{6pt}
\hrule \vspace{6pt}

% Projects
\section*{Projects}

\textbf{Chain Cycle - Blockchain Marketplace} \hfill \href{https://github.com/znafi/Chain-Cycle}{GitHub} \\
\textit{Internet Computer, Motoko, React, TypeScript, Tailwind CSS}
\begin{itemize}[leftmargin=*]
    \item Developed a decentralized marketplace for sustainable material trading using Internet Computer blockchain.
    \item Implemented a token-based reward system (CYC tokens) to incentivize sustainable trading practices.
    \item Built secure user authentication using Internet Identity and created a real-time bidding system.
    \item Designed modular architecture with separate canisters for user profiles, marketplace listings, and token transactions.
\end{itemize}

\textbf{Blood Donation Web Application} \hfill \href{https://bloodinneed.org/}{bloodinneed.org} \\
\textit{React, Material-UI, Node.js, MongoDB}
\begin{itemize}[leftmargin=*]
    \item Developed a full-stack platform for blood donors to register and be searchable by blood type.
    \item Implemented secure authentication using JWT and optimized MongoDB queries for 30\% faster lookups.
    \item Currently has 50+ active donors, assisting with emergency blood needs in Bangladesh.
\end{itemize}

\textbf{Assignment Dashboard} \hfill \href{https://github.com/znafi/Assignment-Tracker.git}{GitHub} \\
\textit{Next.js, Chakra UI, SQLite, Prisma, Vercel}
\begin{itemize}[leftmargin=*]
    \item Designed and developed an assignment tracking system with due date and time tracking features.
    \item Implemented secure JWT-based authentication with HTTP-only cookies.
    \item Optimized database queries for 50\% improved performance.
\end{itemize}

\textbf{Global Legal Reference System} \hfill \href{https://github.com/znafi/Lawyer.git}{GitHub} \\
\textit{Flask, React, SQLAlchemy, Elasticsearch}
\begin{itemize}[leftmargin=*]
    \item Created a web application for searching and accessing constitutional laws worldwide.
    \item Integrated Elasticsearch, enabling instant, keyword-based law lookup.
    \item Built a scalable API with RESTful principles, improving request handling by 40\%.
\end{itemize}

\vspace{6pt}
\hrule \vspace{6pt}

\end{document}
